timesliced_random_cell_selection

### 2018-11-23 src/timesliced_random_cell_selection.Rmd
i thin the backgrond env correlates are in.... 4 days to run loop

First you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
background_all2 <- subset(background_all[1:6, ])
xy <- background_all2[ ,c(7,8)] # This is to tell R where the coordinates are (in column 18 and 19). Note that the column order needs to be longitude, latitude
background_all_sp <- SpatialPointsDataFrame(coords = xy, data = background_all2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
head(background_all_sp)
```

@@

    }
}
head(background_all_sp)
```

>>>>

First you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
xy <- background_all[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
background_all_sp <- SpatialPointsDataFrame(coords = xy, data = background_all, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
head(background_all_sp)
```

@@

    }
}
write.csv(background_all, "../output/bio/background_complete.csv", row.names = FALSE)
head(background_all_sp)
```
